
title: "R Markdown - Frameworks 2 project"
output: html_document
---

This portion of the project focuses on cleaning data, and looking into if there's a correlation between the document's text and amount awarded to each program.

#Define dataset

```{r}
gov_data= AssistanceListings_DataGov_PUBLIC_CURRENT_20190706_AssistanceListings_DataGov_PUBLIC_CURRENT_20190706
```

#Clean Data

```{r}
library(textclean)
library(tidytext)
library(dplyr)
library(tm)
library(splitstackshape)
```

#Split data

```{r}
tokens = c("list","act","description","awarded","lump","other","isApplicable", "est", stopwords)

goodrows = cbind(gov_data[,0:2], gov_data[,37])
rawrows = gov_data[,3:38] 
rawrows$`Obligations (122)` = NULL
rawrows$URL = NULL
Award = gov_data[,25]
```


#Clean award amount column
```{r}
library(splitstackshape)

Award = apply(Award,2,function(x)replace_tokens(x, tokens))
Award = as.data.frame(Award)
Award = cSplit(Award, "Obligations (122)", sep="FY ", type.convert=FALSE)
Award = Award[,3]
Award = apply(Award,2,function(x)substring(x, 3))
Award = apply(Award,2,function(x)strip(x,char.keep = '.',digit.remove = FALSE, apostrophe.remove = FALSE, lower.case = FALSE))
Award = gsub(' ',"",Award)
Award = gsub('.00 ',"",Award)
Award = gsub("[^0-9.-]", "", Award)
Award = apply(Award,2,function(x)as.numeric(x))
Award[is.na(Award)] <- 0
Award = Award[,1]
Award = as.data.frame(Award)
```


#Prepare text columns for corpus
```{r}
corpusdat = do.call(paste, as.data.frame(rawrows, stringsAsFactors=FALSE))
corpusdat = as.data.frame(corpusdat)
gov_data = cbind(goodrows, corpusdat, Award)
```


#Building Corpus
```{r}

corpus = Corpus(VectorSource(gov_data$corpusdat))
corpus = tm_map(corpus,FUN = content_transformer(tolower))
corpus = tm_map(corpus,
                FUN = content_transformer(FUN = function(x)gsub(pattern = 'http[[:alnum:][:punct:]]*',
                                                                replacement = ' ',x = x)))
corpus = tm_map(corpus,FUN = removePunctuation)
corpus = tm_map(corpus,FUN = removeWords,c(stopwords('english')))
corpus = tm_map(corpus,FUN = stripWhitespace)
dtm = DocumentTermMatrix(corpus)
dict = findFreqTerms(DocumentTermMatrix(corpus),
                     lowfreq = 0)
dict_corpus = Corpus(VectorSource(dict))
xdtm = removeSparseTerms(dtm,sparse = 0.95)

dtm_tfidf = DocumentTermMatrix(x=corpus,
                               control = list(weighting=function(x) weightTfIdf(x,normalize=F)))
xdtm_tfidf = removeSparseTerms(dtm_tfidf,sparse = 0.95)
xdtm_tfidf = as.data.frame(as.matrix(xdtm_tfidf))
sort(colSums(xdtm_tfidf),decreasing = T)


xdtm_tfidf = cbind(xdtm_tfidf, Award)
names(xdtm_tfidf) <- make.names(names(xdtm_tfidf))
xdtm_tfidf$X. = NULL

```

#Other tables for analysis
```{r}

library(syuzhet)

syuzhet = as.matrix(apply(rawrows,2,function(x)get_sentiment(x, method = "syuzhet")))
syuzhet = cbind(syuzhet, Award=Award$Award)
syuzhet = as.data.frame(syuzhet)

afinn = as.matrix(apply(rawrows,2,function(x)get_sentiment(x, method = "afinn")))
afinn = cbind(afinn, Award =Award$Award)
afinn = as.data.frame(afinn)

nrc = as.matrix(apply(rawrows,2,function(x)get_sentiment(x, method = "nrc")))
nrc = cbind(nrc, Award= Award$Award)
nrc = as.data.frame(nrc)

bing = as.matrix(apply(rawrows,2,function(x)get_sentiment(x, method = "bing")))
bing = cbind(bing, Award= Award$Award)
bing = as.data.frame(bing)

lengths = as.matrix(apply(rawrows,2,function(x)nchar(x)))
lengths = cbind(lengths, Award=Award$Award)
lengths = as.data.frame(lengths)
lengths[is.na(lengths)] = 0
```

#Methods of eval
```{r}

syuzhet
afinn
nrc
bing
lengths
xdtm_tfidf


#View correlations in document - e.g...
cor(syuzhet, syuzhet$Award)
corrplot(cor(syuzhet))
```

# Predictive Model
```{r}
library(randomForest)
library(caret)

                         
set.seed(522)
split = createDataPartition(y=xdtm_tfidf$Award,p = 0.7,list = F,groups = 100)
train = xdtm_tfidf[split,]
test = xdtm_tfidf[-split,]

rfdt = randomForest(Award~., train)

predForest = predict(rfdt,newdata=test)
rmse = sqrt(mean((predForest - test$Award)^2)) 
plot(rfdt)
```
```